The \prob

### 2013-03-20 byzantine/byzantine.tex
byz: add figures

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\SetAlFnt{\algofont}
\SetAlCapFnt{\algofont}
\SetAlCapNameFnt{\algofont}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}
\renewcommand{\algorithmcfname}{ALGORITHM}

@@

\begin{figure}[h]
	TODO
	\caption{The second friend is a bad guy.}
	\label{fig:1}
\end{figure}
\begin{figure}[h]
	TODO
	\caption{The controlling head is a bad guy.}
	\label{fig:2}
\end{figure}

@@

We show that the Spoken Words plan, with some number $m$, is an answer to the \prob~for more than three times $m$ many heads, as long as there are $m$ or fewer bad guys.

The Spoken Words plan where $m$ is nothing at all (which means there are no bad guys): \begin{enumerate}
	\item The controlling head says what he decided to do to every other head.
	\item Each other head does the thing they heard the controlling head say, or does RUN AWAY if they didn't hear anything.
\end{enumerate}

The Spoken Words plan where $m$ is one more than some other number $j$:
\begin{enumerate}
	\item The controlling head says what he decided to do to every other head.
	\item For each number $i$, let $\fact_i$ be the fact that head number $i$ heard from the controlling head, or else be RUN AWAY if he or she hears nothing. Head number $i$ acts as the controlling-head in the Spoken Word plan for one fewer than $m$, to say $\fact_i$ to the other heads.
	\item For each number $i$, and each number $j$ not the same as $i$, let $\fact_j$ be the fact that head number $i$ heard from head number $j$ in step (2) (using the Spoken Word plan for one fewer than $m$), or else RUN AWAY if they heard nothing. Head number $i$ will do the thing that they heard most often, among all $\fact_j$.
\end{enumerate}

To understand how this plan works, we consider the case where $m$ is one and there are four total heads. Figure~\ref{fig:3} shows what the second head hears when the controlling head says some fact $f$, and the third head is a bad guy.
The third head says some other fact $g$. In step 3, the second head then heard $f$ two times and $g$ once, so decides to do the right thing, which is $f$.

Next, we see what happens if the controlling head is a bad guy. Figure~\ref{fig:4} shows what the other heads hear if the controlling head says whatever he wants, which we'll say are $x$, $y$, and $z$, because they can all be different.
Each other head hears all three different orders, so they all decide to do the same thing in step (3), no matter if $x$, $y$, and $z$ are the same.

@@

\begin{figure}[h]
	TODO
	\caption{Spoken Words plan, where the third head is a bad guy.}
	\label{fig:3}
\end{figure}
\begin{figure}[h]
	TODO
	\caption{Spoken Words plan, where the controlling head is a bad guy.}
	\label{fig:4}
\end{figure}

@@

\begin{figure}[h]
	TODO
	\caption{Signed Letters plan, with the controlling head as a bad guy}
	\label{fig:5}
\end{figure}

>>>>

% Package to generate and customize Algorithm as per ACM style
\usepackage{multirow}
\usepackage{rotating}
\usepackage[ruled]{algorithm2e}
\SetAlFnt{\algofont}
\SetAlCapFnt{\algofont}
\SetAlCapNameFnt{\algofont}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}
\renewcommand{\algorithmcfname}{ALGORITHM}

@@

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.7\textwidth]{fig1.pdf}
	\end{center}
	\caption{The second friend is a bad guy.}
	\label{fig:1}
\end{figure}
\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.75\textwidth]{fig2.pdf}
	\end{center}
	\caption{The controlling head is a bad guy.}
	\label{fig:2}
\end{figure}

@@

We show that the Spoken Words plan, with some number $m$, is an answer to the \prob~for more than three times $m$ many heads, as long as there are $m$ or fewer bad guys.\\

{\em The Spoken Words plan where $m$ is nothing at all (which means there are no bad guys):}\begin{enumerate}
	\item The controlling head says what he decided to do to every other head.
	\item Each other head does the thing they heard the controlling head say, or does RUN AWAY if they didn't hear anything.
\end{enumerate}

{\em The Spoken Words plan where $m$ is one more than some other number $j$:}\begin{enumerate}
	\item The controlling head says what he decided to do to every other head.
	\item For each number $i$, let $\fact_i$ be the fact that head number $i$ heard from the controlling head, or else be RUN AWAY if he or she hears nothing. Head number $i$ acts as the controlling-head in the Spoken Word plan for one fewer than $m$, to say $\fact_i$ to the other heads.
	\item For each number $i$, and each number $j$ not the same as $i$, let $\fact_j$ be the fact that head number $i$ heard from head number $j$ in step (2) (using the Spoken Word plan for one fewer than $m$), or else RUN AWAY if they heard nothing. Head number $i$ will do the thing that they heard most often, among all $\fact_j$.
\end{enumerate}

To understand how this plan works, we consider the case where $m$ is one and there are four total heads. Figure
%\ref{fig:3}
3
shows what the second head hears when the controlling head says some fact $f$, and the third head is a bad guy.
The third head says some other fact $g$. In step 3, the second head then heard $f$ two times and $g$ once, so decides to do the right thing, which is $f$.

Next, we see what happens if the controlling head is a bad guy. Figure
%\ref{fig:4}
4
shows what the other heads hear if the controlling head says whatever he wants, which we'll say are $x$, $y$, and $z$, because they can all be different.
Each other head hears all three different orders, so they all decide to do the same thing in step (3), no matter if $x$, $y$, and $z$ are the same.

@@

\pagebreak
\thispagestyle{empty}
\begin{sideways}
	\begin{tabular}{p{2in}p{9in}p{2in}}
	\vspace{2em}
	\\
	\multicolumn{2}{c}{
		\includegraphics[width=0.9\textwidth]{fig3.pdf}
	}
	&
	\vspace{-8em}
	{\footnotesize Fig. 3. Spoken Words plan, where the third head is a bad guy.}
	\\
	\vspace{2em}
	\\
	\vspace{-10em}
	{\footnotesize Fig. 4. Spoken Words plan, where the controlling head is a bad guy.}
	&
	\multicolumn{2}{c}{
		\includegraphics[width=0.9\textwidth]{fig4.pdf}
	}
	\end{tabular}
\end{sideways}
\pagebreak
\setcounter{figure}{4}

%\begin{figure}[h]
%	%\begin{sideways}\begin{minipage}{\textwidth}
%	\begin{center}
%		\includegraphics[width=0.75\textwidth]{fig3.pdf}
%	\end{center}
%	\caption{Spoken Words plan, where the third head is a bad guy.}
%	\label{fig:3}
%	%\end{minipage}\end{sideways}
%\end{figure}
%\begin{figure}[h]
%	%\begin{sideways}\begin{minipage}{\textwidth}
%	\begin{center}
%		\includegraphics[width=0.75\textwidth]{fig4.pdf}
%	\end{center}
%	\caption{Spoken Words plan, where the controlling head is a bad guy.}
%	\label{fig:4}
%	%\end{minipage}\end{sideways}
%\end{figure}

@@

\begin{figure}[t]
	\begin{center}
		\includegraphics[width=0.7\textwidth]{fig5.pdf}
	\end{center}
	\caption{Signed Letters plan, with the controlling head as a bad guy}
	\label{fig:5}
\end{figure}
